---
title: "MyApp"
author: "Edén Sorolla"
date: "19/8/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, tidy.opts=list(width.cutoff=45), tidy=TRUE)
```


## Covid-19 evolution in Switzerland

This application imports the number of newly infected people and deaths by Covid-19 in the different regions of Switzerland since 31-05-2020.

```{r covid19, echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=45), tidy=TRUE}
require(readxl)
require(httr)
part1 <- "https://github.com/daenuprobst/covid19-cases-switzerland/raw/"
part2 <- "master/covid_19_data_switzerland-phase2.xlsx"
url1 <- paste(part1,part2, sep = "")
GET(url1, write_disk(tf <- tempfile(fileext = ".xlsx")))
df1 <- read_excel(tf, 1) #infected
df2 <- read_excel(tf, 2) #fatalities
```

```{r covid19_2, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, results = "hide", tidy.opts=list(width.cutoff=45), tidy=TRUE}
require(readxl)
require(httr)
part1 <- "https://github.com/daenuprobst/covid19-cases-switzerland/raw/"
part2 <- "master/covid_19_data_switzerland-phase2.xlsx"
url1 <- paste(part1,part2, sep = "")
GET(url1, write_disk(tf <- tempfile(fileext = ".xlsx")))
df1 <- read_excel(tf, 1) #infected
df2 <- read_excel(tf, 2) #fatalities
```

## Slide with Bullets

The application has three main objects:

- Sidebar to choose region and elapsed days since 31-05-2020.
- Dynamic plot changing with date.
- Numeric display of cumulative data.

## Slide with R Output

```{r preprocessing, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
library(chron)
library(tidyr)
library(dplyr)
library(reshape)
library(ggplot2)
library(magrittr) #

df1 <- data.frame(df1[,1:27])
df2 <- data.frame(df2[,1:27])

## We impute the missing values to zero:
for (j in 1:length(df1)){df1[is.na(df1[,j]),j] <- 0}
for (j in 1:length(df2)){df2[is.na(df2[,j]),j] <- 0}

vecNames <- colnames(df1)

df1New <- data.frame(var = cumsum(df1[,2]))

for (i in 3:length(df1)){
    Aux <- data.frame(var = cumsum(df1[,i]))
    df1New <- cbind(df1New, Aux)
}

df1New <- cbind(df1$Date,df1New) #We add the date
colnames(df1New) <- vecNames     #We name the variables
df1New$Date <- as.Date(df1New$Date, format = "%Y-%m-%d") #We coerce the date into Date format

df2New <- data.frame(var = cumsum(df2[,2]))

for (i in 3:length(df2)){
    Aux <- data.frame(var = cumsum(df2[,i]))
    df2New <- cbind(df2New, Aux)
}

df2New <- cbind(df2$Date,df2New) #We add the date
colnames(df2New) <- vecNames     #We name the variables
df2New$Date <- as.Date(df2New$Date, format = "%Y-%m-%d") #We coerce the date into Date format

## We get the data tidy and calculate the accumulated number of infections for each region:
df1New <- melt(df1New, id.vars = c("Date"), measure.vars = colnames(df1)[2:27])
df2New <- melt(df2New, id.vars = c("Date"), measure.vars = colnames(df1)[2:27])

#df1New <- df1New %>%
#    mutate(elapsed.days = as.numeric(difftime(df1New$Date, df1New$Date[1], units = "days")))

colnames(df1New)[2] <- "Region"
colnames(df1New)[3] <- "Cumulative.infected"

colnames(df2New)[2] <- "Region"
colnames(df2New)[3] <- "Cumulative.fatalities"

dfNew <- data.frame(df1New$Date,df1New$Region,df1New$Cumulative.infected,df2New$Cumulative.fatalities)
colnames(dfNew)[1] <- "Date"
colnames(dfNew)[2] <- "Region"
colnames(dfNew)[3] <- "Cumulative.infected"
colnames(dfNew)[4] <- "Cumulative.fatalities"

```

## Slide with Plot

```{r plot, echo = TRUE, warning = FALSE, message = FALSE}
n <- 10
Reg <- "ZH"
selectInf <- dfNew$Cumulative.infected[which(dfNew$Region == Reg)][n]
selectDeath <- dfNew$Cumulative.fatalities[which(dfNew$Region == Reg)][n]
```
